The Morality of Arbitrage

### 2017-05-25 Draft/morality-of-arbitrage.Rmd
Final submission to Mercatus.

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
title: "The Morality of Arbitrage"
author:
- name: Tyler J. Brough
  affiliation: Utah State University
abstract: "In this paper, I argue that one cannot rationally believe that financial arbitrage is an inherently immoral pursuit, while simultaneously believing that the pursuit of academic knowledge is an inherently moral pursuit. I argue that these two seemingly separate activities are really one and the same. Further those that do hold such contradictory beliefs are behaving incoherently and have a Dutch book made against them."
keywords: "arbitrage, Dutch books, morality"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
bibliography: ./master.bib
biblio-style: apsr
---

@@

The paper is organized as follows. I outline an original discussion due to @Coase1974 of the "market for ideas" and the "market for goods," and discuss his conclusion that their different treatment is incongruous in Section 2. I then discuss the idea, due to @Hayek1945, that the economic process is an information process in its most essential treatment in Section 3. In Section 4 I outline the concept of subjective probability following @deFinetti1937, as well as Arbitrage Choice Theory put forward by @Nau1999. In Section 5 I explain the Dutch Book Theorem as essential background to my argument. I give a few chosen examples of scholarly debates framed as Dutch Book arguments in Section 6. In Section 7 I present my own Dutch book argument. Section 8 concludes the paper.

@@

The link between the market for ideas and the market for goods is further strengthened by considering the work of the decision theorist Robert Nau. For example, @NauMcCardle1991 state that the principle of no-arbitrage, which is fundamental in finance theory, is the common foundation of decision theory, game theory and competitive market theory. @Nau1999 refers to this as *arbitrage choice theory* (ACT), following the Bayesian Dutch book arguments of @deFinetti1937. A Dutch book is a situation in which an individual holds incoherent beliefs (beliefs inconsistent with the basic axioms of probability), and if forced to bet on them exposes themselves to a guaranteed loss. When market transactions are seen as knowledge transactions, it becomes clear that a Dutch book is equivalent to arbitrage - the good old fashioned kind often derided from the world of finance. In ACT "... no-arbitage is the core principle of rationality which remains after economic models are stripped of their excess baggage of intrinsically unverifiable or empirically disconfirmed assumptions..." The arbitrageur is Hayek's "man on the spot" who provides a useful informational service by correcting incoherent price signals. This is true in commodities and financial assets as well as in

@@

Coherence in de Finetti's definition of probability is the counterpart of the modern theory of no-arbitrage in finance.[^5] Interestingly, de Finetti took a very operational and economic approach to eliciting subjective probabilities.

The axioms of probability which characterize any theory of probability arise logically from the
condition that subjective probabilities function as prices obeying coherency (i.e. the arbitrage free
conditions).

Looking at problems of uncertainty as situations in which various contingent claims are traded is the key insight offered by the state-preference theory.

The dictionary definition of a Dutch book is the following:

@@

The following example serves to demonstrate the principle. Consider agent A's degree of belief regarding the flipping of a fair coin. The event space is represented by $S = \{H, T\}$ where $H$ represents 'heads' and $T$ represents 'tails.' Suppose A's degrees of belief are expressed as probabilities: $P(H) = 0.51 \quad \mbox{and} \quad P(T) = 0.51$. That is, A is willing to pay $\$0.51$ to receive $\$1$ in the event of a 'heads', and also $\$0.51$ to receive $\$1$ in the event of a 'tails.' It is easy to see that A is acting incoherently. The book maker will be willing to take both bets simultaneously. Either 'heads' or a 'tails' will occur, so if A offers both bets simultaneously she will be guaranteed to earn $\$1$. But the total of her bets is $\$1.02$, so net of her bets she will lose $\$0.02$ whatever the state of the world. A Dutch book has been made against her.

In the nomenclature of finance a Dutch book is an arbitrage and the person making a Dutch book against an opponent is called an arbitrageur. For de Finetti the bookmaker whose gain is certain in a given bet is no different than the trader who earns a guaranteed profit by buying low and selling high when an asset is mispriced.

For de Finetti probabilities are prices. In modern finance theory prices are probabilities. In the end it is an equivalence.

Once seen through the lens of subjective probability, it becomes clear that what applies to mispriced assets also applies to misplaced probabilities. They are both examples of incoherent beliefs.

## Examples of Dutch Book Arguments

- Culp & Miller vs. Pirrong re: whether or not MG was a prudent hedger
- Swinburne vs. Howson re: whether or not God exists

- The morality of scholarship vs the morality of arbitrage is an example of a DBA.

@@

# Conclusion

@@

[^1]: For a book-length treatment of such tendencies on the part of intellectuals see @Sowell2009.
[^2]: Elsewhere @Polanyi2000 has made a similar case.
[^3]: See also @Kreps1988 who states that "the notion that prices contain and convey information is standard doctrine among economists."
[^4]: Hayek wrote: "It is more than a metaphor to describe the price system as a kind of machinery for registering change, or a *system of telecommunications*." Emphasis added. 
[^5]: See @PressaccoZiani2010.
[^x]: @Polanyi2000 makes a similar argument regarding a knowledge problem in science. He writes: "Any attempt to organize the group ... under a single authority would eliminate their independent initiatives, and thus reduce their joint effectiveness to that of the single person directing them from the centre. It would, in effect, paralyse their co-operation." His argument regarding science can be extended to scholarship in general.
[^n]: See the Routledge Dictionary of Economics entry on "Dutch books."

>>>>

---
title: "The Morality of Arbitrage"
author:
- affiliation: Utah State University
  name: Tyler J. Brough
date: "May 25, 2017"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
  html_document: default
  word_document: default
biblio-style: apsr
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
keywords: arbitrage, Dutch books, morality
bibliography: ./master.bib
spacing: double
abstract: In this paper, I argue that one cannot rationally believe that financial
  arbitrage is an inherently immoral pursuit, while simultaneously believing that
  the pursuit of academic knowledge is an inherently moral pursuit. I argue that these
  two seemingly separate activities are really one and the same. Further those that
  do hold such contradictory beliefs are behaving incoherently and have a Dutch book
  made against them.
---

@@

The paper is organized as follows. I outline an original discussion due to @Coase1974 of the "market for ideas" and the "market for goods," and discuss his conclusion that their different treatment is incongruous in Section 2. I then discuss the idea, due to @Hayek1945, that the economic process is an information process in its most essential treatment in Section 3. In Section 4 I outline the concept of subjective probability following @deFinetti1937, as well as arbitrage choice theory put forward by @Nau1999. In Section 5 I explain the Dutch Book Theorem as essential background to my argument. I give a few chosen examples of scholarly debates framed as Dutch Book arguments in Section 6. In Section 7 I present my own Dutch book argument. Section 8 concludes the paper.

@@

The link between the market for ideas and the market for goods is further strengthened by considering the work of the decision theorist Robert Nau. For example, @NauMcCardle1991 state that the principle of no-arbitrage, which is fundamental in finance theory, is the common foundation of decision theory, game theory and competitive market theory. @Nau1999 refers to this as *arbitrage choice theory* (ACT), following the Bayesian Dutch book arguments of @deFinetti1937. A Dutch book is a situation in which an individual holds incoherent beliefs (beliefs inconsistent with the basic axioms of probability), and if forced to bet on them exposes themselves to a guaranteed loss. When market transactions are seen as knowledge transactions, it becomes clear that a Dutch book is equivalent to arbitrage - the good old fashioned kind often derided from the world of finance. In ACT "... no-arbitage is the core principle of rationality which remains after economic models are stripped of their excess baggage of intrinsically unverifiable or empirically disconfirmed assumptions..." The arbitrageur is Hayek's "man on the spot" who provides a useful informational service by correcting incoherent price signals. This is as true for commodities and financial assets as well as for scholarly articles, bestsellers, speeches, and conference presentations.

@@

For de Finetti probability represents the subjective beliefs of the agent. As @Nau2001 explains: "probability does not exist *objectively*, independently of the human mind. [P]robability ... is a rate at which an individual is willing to *bet on* the occurence of an event. Betting rates are the primitive measurements that reveal *your* probabilities or *someone else's* probabilities, which are the only probabilities that really exist." de Finetti took a very operational view of eliciting probabilities. In his theory, "bets are for money, so your probability of an event is effectively the *price* that you are willing to pay for a lottery ticket that yields $1$ unit of money if the event occurs and nothing otherwise." The reader trained in economics or finance will notice the connection to the state-price theory of decision making under uncertainty of @Arrow1964 and @Debreu1959.[^y] Coherence in de Finetti's definition of probability is the counterpart of the modern theory of no-arbitrage in finance.[^5]

The axioms of probability which characterize any valid theory of probability arise logically from the
condition that subjective probabilities function as prices obeying coherency (i.e. the arbitrage free
conditions). Looking at problems of uncertainty as situations in which various contingent claims are traded is the key insight offered by the state-preference theory. ACT differs from the Arrow-Debreu setting in that probabilities and utilities are non-separable, and only de Finetti's *previsions* are observable. In the modern parlance of financial economics these are *risk-neutral probabilities* (the product of state-dependent subjective probabilities and utilities). ACT relaxes the stance of methogological individualism of the neoclassical trading. Rationality characterizes a market-level phenomenon rather than individual behavior. Agents learn to be rational by adopting the market's risk-neutral density as their prior through the market exchange process. The connection to the information process in the Hayekian setting becomes clear: prices convey information and represent agents' subjective beliefs.

With this discussion of subjective probability and ACT as background we can now discuss the Dutch Book Theorem. The dictionary definition of a Dutch book is the following:

@@

The following example serves to demonstrate the principle. Consider agent A's degree of belief regarding the flipping of a fair coin. The event space is represented by $S = \{H, T\}$ where $H$ represents 'heads' and $T$ represents 'tails.' Suppose A's degrees of belief are expressed as probabilities: $P(H) = 0.51 \quad \mbox{and} \quad P(T) = 0.51$. That is, A is willing to pay $\$0.51$ to receive $\$1$ in the event of a 'heads', and also $\$0.51$ to receive $\$1$ in the event of a 'tails.' It is easy to see that A is acting incoherently. The bookmaker will be willing to take both bets simultaneously. Either 'heads' or a 'tails' will occur, so if A offers both bets simultaneously she will be guaranteed to earn $\$1$. But the total of her bets is $\$1.02$, so net of her bets she will lose $\$0.02$ whatever the state of the world. A Dutch book has been made against her.

In the nomenclature of finance a Dutch book is an arbitrage and the person making a Dutch book against an opponent is called an arbitrageur. For de Finetti the bookmaker whose gain is certain in a given bet is no different than the trader who earns a guaranteed profit by buying low and selling high when an asset is mispriced. Once seen through the lens of subjective probability, it becomes clear that what applies to mispriced assets also applies to misplaced probabilities. They are both examples of incoherent beliefs.

According to The Cambridge Dictionary of Philosophy (see @CambDictPhil), the Dutch book theorem can be stated as follows:

> The proposition that anyone who (a) counts a bet on a proposition p as fair if the odds correspond to his degree of belief that p is true and who (b) is willing to make any combinations of bets he would regard individually as fair will be vulnerable to a Dutch book provided his degrees of belief do not conform to the axioms of of the probability calculus. Thus, anyone of whom (a) and (b) are true and whose degree of belief in a disjunction of two incompatible propositions is not equal to the sum of his degrees of belief in the two propositions taken individually would be vulnerable to a Dutch book.

Through the price mechanism and the process of exchange agents's beliefs become coherent as people learn to avoid arbitrage. Again, this is true for security markets and for scholarship. The same market process of *tatonnement* operates in the market for goods and in the market for ideas. Market processes are information processes!

The pursuit of truth that is held as inherently moral in the market for ideas is the same information dynamic that underlies financial and commodity trading. The difference is the relative kinds of knowledge that are processed in the respective markets. While the kinds of knowledge being processed in securities and commodities is more mundane, as Hayek wrote it is no less essential to an efficient, orderly, and rational economic order.

@@

I can now state the main argument of the paper. Given that the "market for goods" and the "market for ideas" are both examples of the same underlying information process: One cannot simultaneously belief that (a) the pursuit of knowledge in scholarship (intellectual arbitrage) is inherently moral, and that (b) the pursuit of trading profits in securities markets (financial arbitrage) is inherently immoral without becoming vulnerable to a Dutch book.

The "market for goods" and the "market for ideas" share a common moral foundation. The same criteria that we use to evaluate one should apply equally to the other.

@@

[^1]: For a book-length treatment of such tendencies on the part of intellectuals see @Sowell2009.
[^2]: Elsewhere @Polanyi2000 has made a similar case.
[^3]: See also @Kreps1988 who states that "the notion that prices contain and convey information is standard doctrine among economists."
[^4]: Hayek wrote: "It is more than a metaphor to describe the price system as a kind of machinery for registering change, or a *system of telecommunications*." Emphasis added. 
[^5]: See @PressaccoZiani2010.
[^x]: @Polanyi2000 makes a similar argument regarding a knowledge problem in science. He writes: "Any attempt to organize the group ... under a single authority would eliminate their independent initiatives, and thus reduce their joint effectiveness to that of the single person directing them from the centre. It would, in effect, paralyse their co-operation." His argument regarding science can be extended to scholarship in general.
[^y]: For a helpful review of state preference theory see Chapter 4 of @CopelandWestonShastri.
[^n]: See the Routledge Dictionary of Economics entry on "Dutch books."

### 2017-05-25 Draft/morality-of-arbitrage.tex
Final submission to Mercatus.

The paper is organized as follows. I outline an original discussion due
to \citet{Coase1974} of the ``market for ideas'' and the ``market for
goods,'' and discuss his conclusion that their different treatment is
incongruous in Section 2. I then discuss the idea, due to
\citet{Hayek1945}, that the economic process is an information process
in its most essential treatment in Section 3. In Section 4 I outline the
concept of subjective probability following \citet{deFinetti1937}, as
well as Arbitrage Choice Theory put forward by \citet{Nau1999}. In
Section 5 I explain the Dutch Book Theorem as essential background to my
argument. I give a few chosen examples of scholarly debates framed as
Dutch Book arguments in Section 6. In Section 7 I present my own Dutch
book argument. Section 8 concludes the paper.

@@

The link between the market for ideas and the market for goods is
further strengthened by considering the work of the decision theorist
Robert Nau. For example, \citet{NauMcCardle1991} state that the
principle of no-arbitrage, which is fundamental in finance theory, is
the common foundation of decision theory, game theory and competitive
market theory. \citet{Nau1999} refers to this as Arbitrage Choice
Theory, following the Bayesian Dutch book arguments of
\citet{deFinetti1937}. A Dutch book is a situation in which an
individual holds incoherent beliefs (beliefs inconsistent with the basic
axioms of probability), and if forced to bet on them exposes themselves
to a guaranteed loss. When market transactions are seen as knowledge
transactions, it becomes clear that a Dutch book is equivalent to
arbitrage - the good old fashioned kind often derided from the world of
finance.

@@

Coherence in de Finetti's definition of probability is the counterpart
of the modern theory of no-arbitrage in finance.\footnote{See
  \citet{PressaccoZiani2010}.} Interestingly, de Finetti took a very
operational and economic approach to eliciting subjective probabilities.

The axioms of probability which characterize any theory of probability
arise logically from the condition that subjective probabilities
function as prices obeying coherency (i.e.~the arbitrage free
conditions).

Looking at problems of uncertainty as situations in which various
contingent claims are traded is the key insight offered by the
state-preference theory.

The dictionary definition of a Dutch book is the following:

@@

The following example serves to demonstrate the principle. Consider
agent A's degree of belief regarding the flipping of a fair coin. The
event space is represented by \(S = \{H, T\}\) where \(H\) represents
`heads' and \(T\) represents `tails.' Suppose A's degrees of belief are
expressed as probabilities:
\(P(H) = 0.51 \quad \mbox{and} \quad P(T) = 0.51\). That is, A is
willing to pay \(\$0.51\) to receive \(\$1\) in the event of a `heads',
and also \(\$0.51\) to receive \(\$1\) in the event of a `tails.' It is
easy to see that A is acting incoherently. The book maker will be
willing to take both bets simultaneously. Either `heads' or a `tails'
will occur, so if A offers both bets simultaneously she will be
guaranteed to earn \(\$1\). But the total of her bets is \(\$1.02\), so
net of her bets she will lose \(\$0.02\) whatever the state of the
world. A Dutch book has been made against her.

In the nomenclature of finance a Dutch book is an arbitrage and the
person making a Dutch book against an opponent is called an arbitrageur.
For de Finetti the bookmaker whose gain is certain in a given bet is no
different than the trader who earns a guaranteed profit by buying low
and selling high when an asset is mispriced.

For de Finetti probabilities are prices. In modern finance theory prices
are probabilities. In the end it is an equivalence.

Once seen through the lens of subjective probability, it becomes clear
that what applies to mispriced assets also applies to misplaced
probabilities. They are both examples of incoherent beliefs.

\subsection{Examples of Dutch Book
Arguments}\label{examples-of-dutch-book-arguments}

\begin{itemize}
\item
  Culp \& Miller vs.~Pirrong re: whether or not MG was a prudent hedger
\item
  Swinburne vs.~Howson re: whether or not God exists
\item
  The morality of scholarship vs the morality of arbitrage is an example
  of a DBA.
\end{itemize}

@@

\section{Conclusion}\label{conclusion}

>>>>

The paper is organized as follows. I outline an original discussion due
to \citet{Coase1974} of the ``market for ideas'' and the ``market for
goods,'' and discuss his conclusion that their different treatment is
incongruous in Section 2. I then discuss the idea, due to
\citet{Hayek1945}, that the economic process is an information process
in its most essential treatment in Section 3. In Section 4 I outline the
concept of subjective probability following \citet{deFinetti1937}, as
well as arbitrage choice theory put forward by \citet{Nau1999}. In
Section 5 I explain the Dutch Book Theorem as essential background to my
argument. I give a few chosen examples of scholarly debates framed as
Dutch Book arguments in Section 6. In Section 7 I present my own Dutch
book argument. Section 8 concludes the paper.

@@

The link between the market for ideas and the market for goods is
further strengthened by considering the work of the decision theorist
Robert Nau. For example, \citet{NauMcCardle1991} state that the
principle of no-arbitrage, which is fundamental in finance theory, is
the common foundation of decision theory, game theory and competitive
market theory. \citet{Nau1999} refers to this as \emph{arbitrage choice
theory} (ACT), following the Bayesian Dutch book arguments of
\citet{deFinetti1937}. A Dutch book is a situation in which an
individual holds incoherent beliefs (beliefs inconsistent with the basic
axioms of probability), and if forced to bet on them exposes themselves
to a guaranteed loss. When market transactions are seen as knowledge
transactions, it becomes clear that a Dutch book is equivalent to
arbitrage - the good old fashioned kind often derided from the world of
finance. In ACT ``\ldots{} no-arbitage is the core principle of
rationality which remains after economic models are stripped of their
excess baggage of intrinsically unverifiable or empirically disconfirmed
assumptions\ldots{}'' The arbitrageur is Hayek's ``man on the spot'' who
provides a useful informational service by correcting incoherent price
signals. This is as true for commodities and financial assets as well as
for scholarly articles, bestsellers, speeches, and conference
presentations.

@@

For de Finetti probability represents the subjective beliefs of the
agent. As \citet{Nau2001} explains: ``probability does not exist
\emph{objectively}, independently of the human mind. {[}P{]}robability
\ldots{} is a rate at which an individual is willing to \emph{bet on}
the occurence of an event. Betting rates are the primitive measurements
that reveal \emph{your} probabilities or \emph{someone else's}
probabilities, which are the only probabilities that really exist.'' de
Finetti took a very operational view of eliciting probabilities. In his
theory, ``bets are for money, so your probability of an event is
effectively the \emph{price} that you are willing to pay for a lottery
ticket that yields \(1\) unit of money if the event occurs and nothing
otherwise.'' The reader trained in economics or finance will notice the
connection to the state-price theory of decision making under
uncertainty of \citet{Arrow1964} and \citet{Debreu1959}.\footnote{For a
  helpful review of state preference theory see Chapter 4 of
  \citet{CopelandWestonShastri}.} Coherence in de Finetti's definition
of probability is the counterpart of the modern theory of no-arbitrage
in finance.\footnote{See \citet{PressaccoZiani2010}.}

The axioms of probability which characterize any valid theory of
probability arise logically from the condition that subjective
probabilities function as prices obeying coherency (i.e.~the arbitrage
free conditions). Looking at problems of uncertainty as situations in
which various contingent claims are traded is the key insight offered by
the state-preference theory. ACT differs from the Arrow-Debreu setting
in that probabilities and utilities are non-separable, and only de
Finetti's \emph{previsions} are observable. In the modern parlance of
financial economics these are \emph{risk-neutral probabilities} (the
product of state-dependent subjective probabilities and utilities). ACT
relaxes the stance of methogological individualism of the neoclassical
trading. Rationality characterizes a market-level phenomenon rather than
individual behavior. Agents learn to be rational by adopting the
market's risk-neutral density as their prior through the market exchange
process. The connection to the information process in the Hayekian
setting becomes clear: prices convey information and represent agents'
subjective beliefs.

With this discussion of subjective probability and ACT as background we
can now discuss the Dutch Book Theorem. The dictionary definition of a
Dutch book is the following:

@@

The following example serves to demonstrate the principle. Consider
agent A's degree of belief regarding the flipping of a fair coin. The
event space is represented by \(S = \{H, T\}\) where \(H\) represents
`heads' and \(T\) represents `tails.' Suppose A's degrees of belief are
expressed as probabilities:
\(P(H) = 0.51 \quad \mbox{and} \quad P(T) = 0.51\). That is, A is
willing to pay \(\$0.51\) to receive \(\$1\) in the event of a `heads',
and also \(\$0.51\) to receive \(\$1\) in the event of a `tails.' It is
easy to see that A is acting incoherently. The bookmaker will be willing
to take both bets simultaneously. Either `heads' or a `tails' will
occur, so if A offers both bets simultaneously she will be guaranteed to
earn \(\$1\). But the total of her bets is \(\$1.02\), so net of her
bets she will lose \(\$0.02\) whatever the state of the world. A Dutch
book has been made against her.

In the nomenclature of finance a Dutch book is an arbitrage and the
person making a Dutch book against an opponent is called an arbitrageur.
For de Finetti the bookmaker whose gain is certain in a given bet is no
different than the trader who earns a guaranteed profit by buying low
and selling high when an asset is mispriced. Once seen through the lens
of subjective probability, it becomes clear that what applies to
mispriced assets also applies to misplaced probabilities. They are both
examples of incoherent beliefs.

According to The Cambridge Dictionary of Philosophy (see
\citet{CambDictPhil}), the Dutch book theorem can be stated as follows:

\begin{quote}
The proposition that anyone who (a) counts a bet on a proposition p as
fair if the odds correspond to his degree of belief that p is true and
who (b) is willing to make any combinations of bets he would regard
individually as fair will be vulnerable to a Dutch book provided his
degrees of belief do not conform to the axioms of of the probability
calculus. Thus, anyone of whom (a) and (b) are true and whose degree of
belief in a disjunction of two incompatible propositions is not equal to
the sum of his degrees of belief in the two propositions taken
individually would be vulnerable to a Dutch book.
\end{quote}

Through the price mechanism and the process of exchange agents's beliefs
become coherent as people learn to avoid arbitrage. Again, this is true
for security markets and for scholarship. The same market process of
\emph{tatonnement} operates in the market for goods and in the market
for ideas. Market processes are information processes!

The pursuit of truth that is held as inherently moral in the market for
ideas is the same information dynamic that underlies financial and
commodity trading. The difference is the relative kinds of knowledge
that are processed in the respective markets. While the kinds of
knowledge being processed in securities and commodities is more mundane,
as Hayek wrote it is no less essential to an efficient, orderly, and
rational economic order.

@@

I can now state the main argument of the paper. Given that the ``market
for goods'' and the ``market for ideas'' are both examples of the same
underlying information process: One cannot simultaneously belief that
(a) the pursuit of knowledge in scholarship (intellectual arbitrage) is
inherently moral, and that (b) the pursuit of trading profits in
securities markets (financial arbitrage) is inherently immoral without
becoming vulnerable to a Dutch book.

The ``market for goods'' and the ``market for ideas'' share a common
moral foundation. The same criteria that we use to evaluate one should
apply equally to the other.
